### 2017-04-18 paper/evaluation.tex
[RQ6] preliminar results

To answer this research question, we considered all six parallel
levels from Section~\ref{sec:modes} and we selected the top 10
projects with long-running tests suites that satisfies the following
criteria: (1) tests run in sequence by default and (2) test suite
consists only by passing tests. The first criteria is to use the
default execution (\ie, configuration \Seq{}) as a baseline to compare
speedup with the other parallel configurations. The second criteria is
to avoid introducing noise when measuring the rate of flakiness caused
by the non-deterministic execution of tests. We are interested only in
failures manifested when parallelism is enabled. Since the number of
failing tests may vary, we run each project three times and report
report the average elapsed time and rate of flakiness.
Figures~\ref{tab:rq6-efficiency} and~\ref{tab:rq6-flaky} summarize the
results obtained.

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakiness}}
\label{tab:rq6-flaky}
\end{figure}

>>>>

To answer this research question, we considered all six parallel
levels from Section~\ref{sec:modes} and we selected the top 10
projects with long-running tests suites that satisfies the following
criteria: (1) tests run in sequence by default and (2) test suite
consists only by passing tests. The first criteria is to use the
default execution (\ie, configuration \Seq{}) as a baseline to compare
speedup with the other parallel configurations. The second criteria is
to avoid introducing noise when measuring the rate of flakiness caused
by the non-deterministic execution of tests. We are interested only in
failures manifested when parallelism is enabled. Since the number of
failing tests may vary, we run each project three times and report the
average elapsed time and rate of flakiness.
Figures~\ref{tab:rq6-efficiency} (ordered by time cost)
and~\ref{tab:rq6-flaky} (ordered by the number of tests) summarize the
obtained results.

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
Kite SDK & - & - & - & - & - & -\\%
Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
OpenMRS Core & - & - & - & - & - & -\\%
Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
Apache Eagle & - & - & - & - & - & -\\%
Geotools & - & - & - & - & - & -\\%
Atomix & - & - & - & - & - & -\\%
Kuromoji & - & - & - & - & - & -\\%
\Fix{Snazy OHC} & - & - & - & - & - & -\\%
\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
Linkedin Pinot & - & - & - & - & - & -\\%
Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
Kite SDK & - & - & - & - & - & -\\%
Apache Giraph & - & - & - & - & - & -\\%
OpenMRS Core & - & - & - & - & - & -\\%
Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
Apache Eagle & - & - & - & - & - & -\\%
Geotools & - & - & - & - & - & -\\%
Atomix & - & - & - & - & - & -\\%
Kuromoji & - & - & - & - & - & -\\%
\Fix{Snazy OHC} & - & - & - & - & - & -\\%
\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakiness}}
\label{tab:rq6-flaky}
\end{figure}
